Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
shortened abstract again

% our field
%  Within the field of mining software repositories, a
Approaches such as topic modeling and concept location rely on the automated application of machine learning algorithms to corpora in order to understand the latent subject matter of software development artifacts.  
% the problem
 Unfortunately, the output of these tools is often difficult to distinguish and interpret. Results are usually abstract, as the topics that are automatically extracted are word-lists lacking semantic interpretation.
% the solution 
 Therefore, in order to have a meaningful discussion about the topics of software development, we must be able to interpret and devise labels for these topics. However, current software engineering topic analysis and concept analysis research relies on manual naming and labelling of topics.
% the labelling research
Furthermore, these topic labelling approaches neither use domain-specific knowledge to improve results, nor contextualize those results for developers.   
% a sub problem
% While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
% what we do
This paper introduces \emph{labelled topic extraction}, in which topics are extracted from commit comments and given labels relating to a cross-project taxonomy. 
% data mining generalizable
Our approach is 
%To ensure we have a 
generalizable and project-agnostic as we label topics using non-functional requirements,
% these qualities 
as these apply across many software systems.% and their development artifacts.
% We used real world data
We evaluated our approach with an experimental study on two large-scale database projects, MySQL and MaxDB. 
% We used LDA, CVS, Bitkeeper
We extracted topics using Latent Dirichlet Allocation (LDA) from the commit-log comments of their version control systems (CVS and BitKeeper). 
% We show NFRs exist
Our results were generalizable across the two projects, showing that non-functional requirements were commonly discussed, and we identified topic trends over time. 	
% we can label stuff
Labelled topic extraction allowed us to devise appropriate, context-sensitive labels across these two projects, providing insight into their software development activities.
\end{abstract}

>>>>

% our field
%  Within the field of mining software repositories, a
To understand the latent subject matter of software development artifacts, researchers have introduced topic modeling and concept location.
These techniques rely on the automated application of machine learning algorithms to corpora.
% the problem
Their outputs are word-lists lacking semantic interpretation, which are difficult to distinguish and interpret. 
%Results are usually abstract, as the topics that are automatically extracted 
% the solution

In order to have a meaningful discussion about the topics of software development, we must be able to interpret and devise labels for these topics. 
%However, current software engineering topic analysis and concept analysis research relies on manual naming and labelling of topics.
% the labelling research
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve results. Nor to they contextualize those results for developers.   
% a sub problem
% While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
% what we do

To solve this problem, this paper introduces \emph{labelled topic extraction}, 
in which topics are extracted from commit comments and given labels relating to a cross-project taxonomy. 
% data mining generalizable
Our approach is 
%To ensure we have a 
generalizable and project-agnostic, as we label topics using non-functional requirements,
% these qualities 
as these apply across many software systems.% and their development artifacts.
% We used real world data
We evaluated our approach with an experimental study on two large-scale database projects, MySQL and MaxDB. 
% We used LDA, CVS, Bitkeeper
We extracted topics using Latent Dirichlet Allocation (LDA) from the commit-log comments of their version control systems (CVS and BitKeeper). 
% We show NFRs exist
%Our results were generalizable across the two projects, showing that non-functional requirements were commonly discussed, 
%and we identified topic trends over time. 	
% we can label stuff
Labelled topic extraction allowed us to devise appropriate, context-sensitive labels across these two projects, providing insight into their software development activities over time.
\end{abstract}
